Tree establishment in models of forest dynamics: a key priority for further research

### 2023-04-26 manuscript/manuscriptRW.Rmd
expading acknowledgement section
small change in the abstract

Using 15 models and model variants built to capture long-term forest
dynamics at the stand, landscape and global levels, we simulate tree
establishment at 200 sites representing large environmental gradients
across Europe. The results are evaluated against comprehensive data from
unmanaged forests.

@@

This paper arises from a workshop held in Davos (Switzerland) in June
2022, co-led by Olalla Díaz-Yáñez, Yannek Käber and Harald Bugmann.
Funding for the workshop was provided by COST Action CA19139 PROCLIAS
(PROcess-based models for CLimate Impact Attribution across Sectors),
supported by COST (European Cooperation in Science and
Technology; [https://www.cost.eu](https://www.cost.eu/)) and ETH Zurich
(Research Grant ETH-35 18-1). ODY was funded by the Swiss National
Science Foundation project 200020_188882 / 1 . KB received support from
the European Research Council under the European Union's Horizon 2020
research and innovation program (Grant Agreement 101001905). JB
acknowledges funding from the long-term research development project no.
RVO 67985939 from the Czech Academy of Sciences. MM acknowledges
financial support from I-Maestro (Innovative forest management
strategies for a resilient bioeconomy under climate change and
disturbances, grant no. 22035418, 2019--2022) funded by the ERA-NET
Cofund ForestValue. MMina acknowledges funding from the H2020-MSCA-IF
project REINFORCE (Grant No. 891671). KM received funding from the
Project No. CZ.02.1.01/0.0/0.0/16_019/0000803 financed by OP RDE, grant
no. ITMS2014+313011W580 supported by the Integrated Infrastructure
Operational Programme funded by the ERDF. CH acknowledges financial
support from Waldfonds WASIM2100 project.

>>>>

Using 15 models and model variants built to capture long-term forest
dynamics at the stand, landscape and global levels, we simulate tree
establishment at 200 sites representing large environmental gradients
across central Europe. The results are evaluated against comprehensive
data from unmanaged forests.

@@

This paper arises from a workshop held in Davos (Switzerland) in June
2022, co-led by Olalla Díaz-Yáñez, Yannek Käber and Harald Bugmann.
Several people on top of the co-authors list have been involved in the
development of this study in several degrees that we would like to thank
here including Martin Gutsch and Giorgio Vacchiano. Funding for the
workshop was provided by COST Action CA19139 PROCLIAS (PROcess-based
models for CLimate Impact Attribution across Sectors), supported by COST
(European Cooperation in Science and
Technology; [https://www.cost.eu](https://www.cost.eu/)) and ETH Zurich
(Research Grant ETH-35 18-1). ODY was funded by the Swiss National
Science Foundation project 200020_188882 / 1 . KB received support from
the European Research Council under the European Union's Horizon 2020
research and innovation program (Grant Agreement 101001905). JB
acknowledges funding from the long-term research development project no.
RVO 67985939 from the Czech Academy of Sciences. MM acknowledges
financial support from I-Maestro (Innovative forest management
strategies for a resilient bioeconomy under climate change and
disturbances, grant no. 22035418, 2019--2022) funded by the ERA-NET
Cofund ForestValue. MMina acknowledges funding from the H2020-MSCA-IF
project REINFORCE (Grant No. 891671). KM received funding from the
Project No. CZ.02.1.01/0.0/0.0/16_019/0000803 financed by OP RDE, grant
no. ITMS2014+313011W580 supported by the Integrated Infrastructure
Operational Programme funded by the ERDF. CH acknowledges financial
support from Waldfonds WASIM2100 project.
